### 2020-02-07 README.Rmd
Fix typos

The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia. It is very popular in Taiwan, Japan and Hong Kong] is to generate and adminstrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.

>>>>

The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia. It is very popular in Taiwan, Japan and Hong Kong] is to generate and administrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
